The \textit{Kepler} Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-07 paper/ms.tex
33 red giants

% Abstract of the paper
\begin{abstract}
We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this paper, aside from publishing the light curves of these stars, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 34 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars. We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo from these collateral data, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only one~G dwarf. We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 34~red giants. We do not model main-sequence stars in great detail, but provide some discussion and initial classification of interesting variability. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements. We have also obtained high-resolution optical spectroscopy of 63~stars, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph \citep[TRES;][]{2007RMxAC..28..129S}. For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

Among the~66 red giants identified in this sample, for~32 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics which are hard to correct with the CBV approach. In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs). For the~34 giants for with high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters through the approximate scaling relations:

@@

We obtained good estimates of these asteroseismic parameters for 34 targets, presented in Table~\ref{astero_table}. In the remainder of cases, as noted above, very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we were not able to obtain good estimates for these stars.

@@

We determined the mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table~\ref{astero_table}) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}. \textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy} with overshooting and no mass-loss.

@@

@@

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. BJSP also acknowledges support from Balliol College and the Clarendon Fund. DH acknowledges support by the National Aeronautics and Space Administration through the K2 Guest Observer Program (NNX17AF76G, 80NSSC18K0362) and the National Science Foundation (AST-1717000). TRW acknowledges the support of the Australian Research Council (grant DP150100250). DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory. The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No670519: MAMSIE). VSA acknowledges support the Independent Research Fund Denmark (Research grant 7027-00096B). Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement No.~DNRF106). PJ acknowledges FONDECYT Iniciaci\'on grant 11170174.

BJSP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples. We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands. We would like to acknowledge the Gadigal Clan of the Eora Nation as the traditional owners of the land on which the University of Sydney is built and on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.

>>>>

% Abstract of the paper
\begin{abstract}
We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this paper, aside from publishing the light curves of these stars, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 33 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars. We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo from these collateral data, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only one~G dwarf. We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 33~red giants. We do not model main-sequence stars in great detail, but provide some discussion and initial classification of interesting variability. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements. We have also obtained high-resolution optical spectroscopy of 63~stars, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph \citep[TRES;][]{2007RMxAC..28..129S}. For the~33 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

Among the~66 red giants identified in this sample, for~32 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics which are hard to correct with the CBV approach. In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs). For the~33 giants for with high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters through the approximate scaling relations:

@@

We obtained good estimates of these asteroseismic parameters for 33 targets, presented in Table~\ref{astero_table}. In the remainder of cases, as noted above, very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we were not able to obtain good estimates for these stars.

@@

We determined the mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table~\ref{astero_table}) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}. \textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy}. No diffusion or rotational mixing was included, while core overshoot with an efficiency of 0.20 times the pressure scale height as described in \citet{Hidalgo:2018dy}.

@@

To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax. We find that there is a dramatic improvement in the precision of the stellar radii determined here: some stars which did not previously have radii now have precise radii, and for those inferred from \gaia, the new radii are much more precise.

@@

\begin{figure}
\noindent\includegraphics[width=8.5cm,keepaspectratio]{gaia_comparison.eps}

\caption{\label{gaia_comparison}
A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue. The precision of the new radii from stellar modelling are a dramatic improvement on those from \gaia. }
\end{figure}

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. BJSP also acknowledges support from Balliol College and the Clarendon Fund. DH acknowledges support by the National Aeronautics and Space Administration through the K2 Guest Observer Program (NNX17AF76G, 80NSSC18K0362) and the National Science Foundation (AST-1717000). TRW acknowledges the support of the Australian Research Council (grant DP150100250). TRW and VSA acknowledge
the support of the Villum Foundation (research grant 10118). DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory. The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No670519: MAMSIE). VSA acknowledges support the Independent Research Fund Denmark (Research grant 7027-00096B). Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement No.~DNRF106). PJ acknowledges FONDECYT Iniciaci\'on grant 11170174.

% BJSP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples. We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands. We would like to acknowledge the Gadigal Clan of the Eora Nation as the traditional owners of the land on which the University of Sydney is built and on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future. %% Take this out for MNRAS
